---
title: "Project proposal"
author: "The Mousebreakers"
output: github_document
---

```{r load-packages, message = FALSE}
library(tidyverse)
library(broom)


astronauts <- read_csv("/cloud/project/data/astronauts.csv")

```

## 1. Introduction
As a team, we have decided to use the dataset `astronauts` as we believe we can construct a meaningful analysis of this data and draw valuable conclusions. This dataframe contains information about the astronauts that have been on various space expeditions overtime. It contains data on their sex, what year they were selected, what year their mission launched, how long they spent in space, if they were in the military or a civilian, if they completed additional missions, and many other variables. 

We are going to specifically analyse the gender equality of the astronaut profession; how has the ratio of male to female astronauts changed over time? We'll be taking into account factors such as nationality, occupation, military status, time spent in space and mean total number of missions. The STEM industry is known for being heavily male dominated; although that is starting to change, to what extent? Are there certain factors or areas in which progress is being inhibited, and can these barriers be overcome? The characteristic we are going to focus our study around is the employment of women over time in the space industry.

Our data is from TidyTuesday's Astronaut Database with the data was collected from those who have traveled to space. There is a variety of data variables collected from occupation, number of hours in space, number of missions to year and sex. 
The main aspect we going to focus on is gender equality in  the space industry and if this has changed over time. This industry is known for being male dominated and we are going to analyse if there have been more females employed in the industry overtime.

## 2. Data
```{r see_data}
glimpse(astronauts)
```


## 3. Data analysis plan

The outcome will be the variables that we will be looking at (i.e. occupation, number of missions, military status, time spent in space etc.). The predictor will be the sex of the astronauts and we will evaluate this over time. 

```{r year_and_sex}
astronauts %>%
  ggplot(aes(x = year_of_selection, fill = sex)) + 
  geom_bar()

astronauts %>%
  ggplot(aes(x = year_of_selection, fill = sex)) + 
  geom_bar(position = "fill")

```


```{r number_of_missions}
astronauts %>%
  summarise(n_distinct(mission_title))
```

The total number of missions covered in this data set is `r astronauts %>% summarise(n_distinct(mission_title))`.



```{r mean_total_missions}
# mean of total number of missions for male vs female astronauts
astronauts %>%
  group_by(sex) %>%
  summarise(
    mean_n = mean(total_number_of_missions)
  ) 
```

