---
title: "Project proposal"
author: "The Mousebreakers"
output: github_document
---

```{r load-packages, message = FALSE}
library(tidyverse)
library(broom)


astronauts <- read_csv("/cloud/project/data/astronauts.csv")

```

## 1. Introduction
As a team, we have decided to use the dataset `astronauts` as we believe we can construct a meaningful analysis of this data and draw valuable conclusions. This dataframe contains information about astronauts that have been on various space expeditions over time, such as their sex, what year they were selected, what year their mission launched, how long they spent in space, if they were in the military or a civilian, if they completed additional missions, and many other variables. 

We are going to specifically analyse gender equality among astronauts; how has the ratio of male to female astronauts changed over time? We'll be taking into account factors such as nationality, occupation, military status, time spent in space and mean total number of missions. The STEM industry is known for being heavily male dominated; although that is starting to change, to what extent? Are there certain factors or areas in which progress is being inhibited, and can these barriers be overcome? The characteristic we are going to focus our study around is the employment of women over time in the space industry.

Our data is from TidyTuesday's Astronaut Database, with the data collected solely about those who have travelled to space. There exists a wide variety of data variables available for analysis; we will select the ones we used carefully, as not all may be relevant to our objective.


## 2. Data
```{r see_data}
glimpse(astronauts)
```


## 3. Data analysis plan

The outcome will be the variables that we will be looking at (i.e. occupation, number of missions, military status, time spent in space etc.). The predictor will be the sex of the astronauts and we will evaluate this over time. The conclusion that we want to come to is that, while the astronautical industry was sexist and biased towards men in the past, in recent times this has changed; women are now given equal opportunities and regarded with the same respect as male astronauts. This will present itself in the data through more equal gender ratios, longer mission times for women and more junior women in the military being sent to space.

```{r year_and_sex}
astronauts %>%
  ggplot(aes(x = year_of_selection, fill = sex)) + 
  geom_bar()+
  labs(title = "The number of astronauts selected for missions over time, by gender",
       x = "Year of selection",
       y = "Number of astronauts",
       caption = "Data from TidyTuesday's Astronaut Database")+
  theme(legend.title = element_blank()) +
   theme(plot.margin = unit(c(1, 1, 1, 1),"cm"))


astronauts %>%
  ggplot(aes(x = year_of_selection, fill = sex)) + 
  geom_bar(position = "fill")+
  labs(title = "The proportion of male/female astronauts selected for missions over time",
       x = "Year of selection",
       y = "Percentage of male/female astronauts",
       caption = "Data from TidyTuesday's Astronaut Database")+
  theme(legend.title = element_blank())+
  scale_y_continuous(labels = scales::percent) +
   theme(plot.margin = unit(c(1, 1, 1, 1),"cm"))



```


```{r number_of_missions}
astronauts %>%
  summarise(n_distinct(mission_title))
```

The total number of missions covered in this data set is `r astronauts %>% summarise(n_distinct(mission_title))`.



```{r mean_total_missions}
# mean of total number of missions for male vs female astronauts
astronauts %>%
  group_by(sex) %>%
  summarise(
    mean_n = mean(total_number_of_missions)
  ) 
```




```{r}

```

